Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-02 ProbabilisticCoherence.tex
Changed  discussion of R matrix

We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$. We also note that when $\bm{S}$ is understood as a linear mapping $\bm{S}:\mathbb{R}^m\rightarrow\mathbb{R}^n$ whose image given by the coherent space $\mathfrak{s}$. This is depicted in Figure~\ref{fig2}.

@@

Using Definition~\ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation. Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$. Note that $\bm{R}$ is not unique; one example is a matrix whose columns represent the aggregation constraints for a given hierarchy. For the hierarchy in example 1, 
$$ 
\bm{S} = 
\begin{pmatrix} 
1& 1 \\ 1 & 0 \\ 0&1 
\end{pmatrix} 
\quad \text{and} \quad 
\bm{R} = 
\begin{pmatrix}  
1 \\ -1 \\ -1 
\end{pmatrix}.
$$

Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

>>>>

We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}_\perp=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$. We also note that when $\bm{S}$ is understood as a linear mapping $\bm{S}:\mathbb{R}^m\rightarrow\mathbb{R}^n$ whose image given by the coherent space $\mathfrak{s}$. This is depicted in Figure~\ref{fig2}.

@@

Definition~\ref{def:reconpoint}, in fact defines an entire family of forecast reconciliation methods including many methods currently extant in the literature. To provide a geometric interpretation, we introduce an $\mathbb{R}^{n \times (n-m)}$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$. The columns of $\bm{R}$ can be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space. 
A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$.  This vector is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
%$$ 
%\bm{S} = 
%\begin{pmatrix} 
%1& 1 \\ 1 & 0 \\ 0&1 
%\end{pmatrix} 
%\quad \text{and} \quad 
%\bm{R} = 
%\begin{pmatrix}  
%1 \\ -1 \\ -1 
%\end{pmatrix}.
%$$ 
%
%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.
